DTOADQ

### 2017-10-22 documentation/paper.tex
almost done with bpt just need mis
working on bdpt

  \begin{align}
    P = \frac{1.0f}{N} \Sigma_{0}^{\infty} \Sigma_{s \le 0} \Sigma_{t \le 0}
    \alpha^L_s c_{s,t} \alpha^E_t MIS_{s, t}(\bar{y}, \bar{z})
  \end{align}

@@

>>>>

  \begin{align}
    P = \frac{1.0f}{N} \Sigma_{0}^{N} \Sigma_{s \le 0} \Sigma_{t \le 0}
    \alpha^L_s c_{s,t} \alpha^E_t MIS_{s, t}(\bar{y}, \bar{z})
  \end{align}

@@

        // What's defined: V1 -> V2 [we're evaluating V1] This is for a lens.
        // So, it's ultimately completely useless until an
        // actual lens exists in the SDF scene. Note that this isn't an actual
        // point on a surface of the scene (that's V2, next up for eval), this
        // is just an infinitesimal point based off where the camera currently
        // is, just like a delta light. So while the point actually exists on a
        // scene, the evaluation is on a "delta camera"
